% Caitlin Kramer's super duper resume

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{#1}}%
  \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{-0.5#1}}%
  \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  #1 &
  #2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Caitlin Kramer}}

45 Cherokee Street Apt. 1\ \ $\diamond$
\ Boston, MA 02120
\\
(321) 266-6642\ \ $\diamond$
\ kramer.ca@husky.neu.edu
\end{center}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
      {\textbf{Northeastern University}}
      {\textbf{Boston, MA}}
  \\
  \headerrow
      {\emph{College of Science, B.S./M.S. Chemistry}}
      {\emph{2011 - 2016}}

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
  \parskip=0.1em

\item
  \headerrow
      {\textbf{DNA Damage Recognition and Tolerance Laboratory}}
      {\textbf{Northeastern University}}
  \\
  \headerrow
      {\emph{MS Student, previously Undergraduate Researcher}}
      {\emph{May 2012 -- Present}}
      Supervised by Dr. Penny Beuning
    \begin{itemize*}
    \item Developed protocols for expression and purification of multiple proteins.
    \item Led research on the uncharacterized \emph{E. coli}
      DNA damage response gene \emph{ybfE} and confirmed a
      computational prediction of DNA binding using
      \emph{in vitro} methods. Structurally
      characterized the protein using site-directed
      mutagenesis, circular dichroism, and molecular
      modeling. Conducted \emph{in vivo} assays
      to elucidate the gene's functional role.
    \item Investigated the putative Y-family DNA polymerase
      DinB from plant symbiont \emph{Sinorhizobium meliloti}.
      Cloned gene into pET expression vector. Troubleshot problems with protein
      solubility to acquire viable protein for characterization. Assayed protein
      activity by primer extension.
    \item Designed experimental protocols for damaging DNA \emph{in vivo} and
      \emph{in vitro} with nitrofurazone and benzyl bromide. Prepared  samples for LC-MS
      characterization of resulting adducts.
    \item Mentored and trained undergraduate students in the lab.
    \end{itemize*}

\item
  \headerrow
      {\textbf{GlaxoSmithKline}}
      {\textbf{Boston MDR}}
  \\
  \headerrow
      {\emph{Library Chemistry Co-op}}
      {\emph{January 2013 -- June 2013}}
      Supervised by Dr. Josephine Yuen
    \begin{itemize*}
    \item Participated in development work, production, and quality
      control of a 49 million member purine-scaffold library using
      ELT (Encoded Library Technology).
    \item Ensured general reaction scheme was valid prior to library
      production.
    \item Checked that ligation of DNA tags was not impeded by other
      reactants.
    \item Determined the scope of reactive chemical building blocks to
      be used in production.
    \end{itemize*}

\item
  \headerrow
      {\textbf{InfoCommons Service Desk}}
      {\textbf{Northeastern University}}
  \\
  \headerrow
      {\emph{Student Staff}}
      {\emph{September 2011 -- Present}}
      Supervised by Mike Horgan
    \begin{itemize*}
    \item Assisted customers in person and on the phone with addressing
      computer problems on personal and lab computers.
    \item Kept printers and lab computers in working order.
    \item Communicated with managers to provide the most up-to-date
          information to customers and other staff.
    \end{itemize*}
\end{itemize}
\hrule
\vspace{-0.4em}

\subsection*{Skills and Qualifications}

%% \begin{indentsection}{\parindent}
%% \hyphenpenalty=1000
\begin{itemize}
  \item \textbf{Chemical biology:}
    PCR, site-directed mutagenesis, molecular cloning,
    gel electrophoresis, Western Blot, protein expression (including pET
    system) and purification (AKTA), primer extension
  (\textsuperscript{32}P), differential scanning fluorimetry, DNA
    purification, cell culture, sterile technique, bacterial
    transformation, sequencing data analysis
   %% \vspace{0.2em}
  \item \textbf{Analytical:}
    Circular dichroism, NMR (Varian), LC-MS, HPLC, UV/Vis, IR, TLC, data analysis
  %% \vspace{0.2em}
  \item \textbf{Organic:}
    Crystallization, separation, extraction, distillation, TLC,
    anhydrous technique, purification, characterization, library constuction,
    quality control
  %% \vspace{0.2em}
  \item \textbf{Computer:}
    Linux, PC, Mac, Office suite, SQL, Racket, Python, emacs, LaTeX,
    Pymol, YASARA, Entrez Direct, EndNote
\end{itemize}
%% \end{indentsection}


\hrule
\vspace{-0.4em}
\subsection*{Conferences and Presentations}

\begin{itemize}
  \parskip=0.1em

\item Matz Research Symposium 2015 $\diamond$  20 minute oral presentation given to Northeastern
  alumni, faculty and students.
\item ASBMB 2015 Annual Meeting $\diamond$ Boston.
  Presented poster: ``Expression and purification of
  putative Y-family polymerase DinB from \emph{Sinorhizobium meliloti}''
\item ASBMB 2016 Annual Meeting $\diamond$ San Diego.
  Presenting poster: ``Characterization of the \emph{E. coli} SOS
  response protein YbfE''

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Awards}

\begin{itemize}
  \parskip=0.1em

\item Matz Research Scholarship $\diamond$ 2014. Competitive grant
  given to undergraduates used to fund 6 month full-time research
  co-op.
\item Provost Thesis Grant $\diamond$ 2015. Funding awarded
  selectively to graduate students based on written proposals.

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Affiliations}

\begin{itemize}
  \parskip=0.1em

\item American Chemical Society, since 2015
\item American Society for Biochemistry and Molecular Biology, since
  2015.

\end{itemize}

\end{document}
